---
title: "TITLE" #change title here
subtitle: "SUBTITLE" #change subtitle here
author: "Nachname, Vorname"
mail: "uk123456@student.uni-kassel.de"
date: "XX/XX/202X" #change date here
location: "Kassel"
subject: "ABC - X. Fachsemester"
subject2: "XYZ - X. Fachsemester"
matriculation_number: "12345678"
university: "Universität Kassel"
lecturer: "Frau / Herr / Dr. / Prof. "
faculty: "Fachbereich 05 Geselschaftswissenschaften"
module : "NAME MODUL"
class: "NAME KURS"
output: 
  pdf_document:
    toc_depth: 5
    number_sections: true 
    pandoc_args:
      - --lua-filter=scripts/first-line-indent.lua
      - --lua-filter=scripts/wordcount.lua
      - --metadata=wordcount=process
    latex_engine: xelatex #xelatex #lualatex #pdflatex
    includes:
      in_header: styles/preamble.tex #include styling
    keep_tex: false
  bookdown::pdf_book:
    citation_package: biblatex  #natbib #biblatex
bibliography: ["`r paste(list.files(path = 'bib', pattern = '^.+\\.bib$', full.names = TRUE), collapse='\",\"')`"]
csl: styles/csl.csl #include citation styleing
lang: de #change language here
fontsize: 12pt #change font size here #max=12
urlcolor: "magenta"
---

<!-- this chunk is your setup-chunk  -->

```{r setup, include=FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

library(tidyverse)

# get information from YAML header
yaml <- rmarkdown::yaml_front_matter("index.Rmd")


knitr::knit_hooks$set(
  inline = function(x) {
    if (!is.numeric(x)) {
      x
    } else{
      prettyNum(round(x, 2), big.mark = " ")
    }
  }
)

options("scipen" = 100, "digits" = 4)

options(qwraps2_markup = "latex") #markdown

theme_set(theme_classic())
```


<!-- automatically create a bib database for R packages -->

```{r include=FALSE}
knitr::write_bib(c(.packages(), 'knitr', 'rmarkdown'),
                 'bib/packages.bib')
```

<!-- load data -->

```{r}
data(starwars) #example dataframe
```

<!-- include title -->
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.0pt}
\pagenumbering{gobble}

<!-- begin title -->
\thispagestyle{empty}
```{r, child=c('children/000title.rmd')}
```
\pagebreak
<!-- end title -->

<!-- set header options -->
\fancyfoot{}
\fancyhead[R]{\thepage}



<!-- include abstract -->

\setstretch{1.5} <!-- line spaceing 1.5-->
```{r, child=c('children/002abstract.Rmd')}
```
\pagebreak
<!-- include list of abbreviations lof, lot, toc -->

\setstretch{1}
\pagenumbering{roman} <!-- set page numbering to roman numbers -->

\listoffigures
\pagebreak

\listoftables
\pagebreak

\printacronyms[name=Abkürzungsverzeichnis]
\addcontentsline{toc}{section}{Abkürzungsverzeichnis}
\pagebreak

\setcounter{tocdepth}{`r paste0(yaml$output$pdf_document$toc_depth)`}
\tableofcontents
\pagebreak


<!-- begin body -->
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\setstretch{1.5} <!-- set line spaceing -->

<!-- include chapter / children -->
```{r, child=c('children/010introduction.rmd', 'children/020literature_review.rmd', 'children/030hypotheses.rmd', 'children/040operationalization.rmd', 'children/050analysis.rmd', 'children/060conclusion.rmd')}
```
<!-- end body -->


<!-- inlude bibliography -->
\pagebreak
\fancyhead{}
\fancyhead[R]{\thepage}
# Literaturverzeichnis {-}
<div id="refs"></div>

<!-- include apendix -->

\pagebreak
\pagenumbering{gobble}

# Anhang {-}

\thispagestyle{empty}
\pagenumbering{gobble}

```{r, child=c('children/999apendix.Rmd')}
```
