---
output:
  pdf_document:
    number_sections: true
    pandoc_args:
      - --lua-filter=wordcount.lua
      - --metadata=wordcount=process
    latex_engine: pdflatex #xelatex #lualatex #pdflatex
    includes:
      in_header: styles/preamble.tex #include styling
    keep_tex:  true
  always_allow_html: true
  bookdown::pdf_book:
    citation_package: biblatex  #natbib #biblatex
bibliography: ["`r paste0(list.files(path = 'bib', pattern = '^.+\\.bib$', full.names = TRUE), collapse='\",\"')`"]
csl: styles/my.csl #include citation styleing
lang: de #change language here
fontsize: 12pt #change font size here #max=12
urlcolor: "blue"
#nocite: '@*'
#nocite: |
#  @key1, @key2
---

```{r setup, include=FALSE}
 knitr::opts_chunk$set(
 echo = FALSE,
 message = FALSE,
 warning = FALSE
 )
```

```{r}
# automaticly install + library all packages 
packages <- c("tidyverse", "stargazer") 

installed_packages <- packages %in% rownames(installed.packages())

if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

invisible(lapply(packages, library, character.only = TRUE))
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), 'knitr', 'rmarkdown'),
                 'bib/packages.bib')
```

<!-- begin title -->
\pagenumbering{gobble}
```{r, child=c('children/title.Rmd')}
```
\pagebreak
\afterpage{\blankpage}
<!-- end title -->

<!-- begin list of content -->
\setstretch{1}
\pagenumbering{roman}

\pagebreak
\afterpage{\blankpage}

\listoffigures

\pagebreak
\afterpage{\blankpage}

\listoftables

\pagebreak
\afterpage{\blankpage}

\tableofcontents

\pagebreak
\afterpage{\blankpage}
<!-- end list of content -->

\setstretch{1.5} <!-- line spaceing 1.5-->

<!-- begin abstract -->
\pagenumbering{gobble}
```{r, child=c('children/abstract.Rmd')}
```
\pagebreak
<!-- end abstract -->

<!-- begin body -->
\pagenumbering{arabic}
```{r, child=c('children/introduction.rmd', 'children/literature_review.rmd', 'children/hypotheses.rmd', 'children/operationalization.rmd', 'children/analysis.rmd', 'children/conclusion.rmd')}
```
<!-- end body -->


<!-- inlude bibliography -->
\pagebreak
# Literaturverzeichnis 
<div id="refs"></div>

<!-- inlude apendix -->
\pagebreak
\pagenumbering{gobble}

# Anhang {-}
\thispagestyle{empty}
\pagenumbering{gobble}
